Journal

### 2024-11-22 Journal/notes.tex
Progress on finsler approach

>>>>

  \subsection*{Finsler's Lemma workaround}

  A way to try and solve the problem was to use a different matrix for the ETM. For the $i^{th}$ layer it was used the following matrix so far:

  $$    
    \bmx{
      \tilde{x}\\
      \tilde{\psi_{i}}\\
      \tilde{\nu_{i}}
    }\tr
    \Omega_{i}
    \bmx{
      \tilde{x}\\
      \tilde{\psi_{i}}\\
      \tilde{\nu_{i}}
    } = \bmx{
      \tilde{x}\\
      \tilde{\psi_{i}}\\
      \tilde{\nu_{i}}
    }\tr
    \bmx{
      0 & 0 & 0\\
      T_{i} G_{i} & T_{i} & -T_{i}\\
      0 & 0 & 0 
    }
    \bmx{
      \tilde{x}\\
      \tilde{\psi_{i}}\\
      \tilde{\nu_{i}}
    }
  $$

  With $TG = Z$ to address the bilinear term. Due to the sparseness of $\Omega$ we want to find a denser matrix $X$ that approximates $\Omega$ and is compliant with the Finsler's Lemma. It can be done by adding the following constraint in the LMI:

  $$
  \Omega = \bmx{
    \begin{array}{ccc|ccc|ccc}
      0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
      Z_{1} & T_{1} & -T_{1} & 0 & 0 & 0 & 0 & 0 & 0\\
      0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
      \hline
      0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
      0 & 0 & 0 & Z_{2} & T_{2} & -T_{2} & 0 & 0 & 0\\
      0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
      \hline
      0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
      0 & 0 & 0 & 0 & 0 & 0 & Z_{3} & T_{3} & -T_{3}\\
      0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
    \end{array}
  }
$$

$$
  X = \bmx{
    \begin{array}{c|c|c}
      X_{1} & 0 & 0\\
      \hline
      0 & X_{2} & 0\\
      \hline
      0 & 0 & X_{3}
    \end{array}
  }
$$

$$
R_{\xi}\tr He\left\{ X - \Omega \right\} R_{\xi} + He \left\{  \pmx{N_{1} \\ N_{2} \\ N_{3}} \pmx{R N_{\nu x} & \Id - R & -\Id} \right\} \leq 0
$$

The matrix $R_{\xi}$ orders the vector that should be multiplied by $X$ and $\Omega$:

$$
     \bmx{
      \tilde{x}\\
      \tilde{\psi}\\
      \tilde{\nu}
     } = \bmx{
      \tilde{x}\\
      \tilde{\psi_{1}}\\
      \tilde{\psi_{2}}\\
      \tilde{\psi_{3}}\\
      \tilde{\nu_{1}}\\
      \tilde{\nu_{2}}\\
      \tilde{\nu_{3}}
    } = \bmx{
      \tilde{x}\\
      \tilde{\psi_{1}}\\
      \tilde{\nu_{1}}\\
      \tilde{x}\\
      \tilde{\psi_{2}}\\
      \tilde{\nu_{2}}\\
      \tilde{x}\\
      \tilde{\psi_{3}}\\
      \tilde{\nu_{3}}
    } R_{\xi} = \bmx{
      \tilde{x}\\
      \tilde{\psi_{1}}\\
      \tilde{\nu_{1}}\\
      \tilde{x}\\
      \tilde{\psi_{2}}\\
      \tilde{\nu_{2}}\\
      \tilde{x}\\
      \tilde{\psi_{3}}\\
      \tilde{\nu_{3}}
    } \bmx{
      \Id & 0 & 0 & 0 & 0 & 0 & 0\\
      0 & \Id & 0 & 0 & 0 & 0 & 0\\
      0 & 0 & 0 & 0 & \Id & 0 & 0\\
      0 & 0 & 0 & 0 & 0 & 0 & 0\\
      0 & 0 & \Id & 0 & 0 & 0 & 0\\
      0 & 0 & 0 & 0 & 0 & \Id & 0\\
      0 & 0 & 0 & 0 & 0 & 0 & 0\\
      0 & 0 & 0 & \Id & 0 & 0 & 0\\
      0 & 0 & 0 & 0 & 0 & 0 & \Id
    } 
$$

With this condensed notation I proceed to discuss the sign of the increment of the Lyapunov function $\Delta V$. I start by plugging the ETM condition, further considerations on the proper sector conditions will be done later. Now the matrix $X$ is used instead of $\Omega$:

\begin{align*}
  \Delta V &= (\tilde{x}^{+})\tr P (\tilde{x}^{+}) + He\left\{ \one\tr \eta^{+} \right\} - \tilde{x}\tr P \tilde{x} - He\left\{ \one\tr \eta \right\} =\\
  &= \left( A \tilde{x} + B \tilde{u} + C \tilde{\phi} \right)\tr P \left( A \tilde{x} + B \tilde{u} + C \tilde{\phi} \right) - \tilde{x}\tr P \tilde{x} + He\left\{ \one\tr \left(   \left( R + L \right)\eta - X \one - \eta  \right) \right\} = \\
  &= \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  }\tr \bmx{
    \bar{A}\tr P \bar{A} - P & \bar{A}\tr P \bar{B} & \bar{A}\tr P C \\
    \bar{B}\tr P \bar{A} & \bar{B}\tr P \bar{B} & \bar{B}\tr P C \\
    C\tr P \bar{A} & C\tr P \bar{B} & C\tr P C
  } \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  } + He\left\{ \one\tr \left( \left( R + L - I \right) \eta - X \one \right) \right\} =
\end{align*}

I can synthesize the ETM condition rewriting something like: $X \one \geq R \eta$ that holds element-wise. I can then exploit $\eta \leq R^{-1} X \one$ and plug it in $\Delta V$ to get rid of $\eta$:

\begin{align*}
  \Delta V &= \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  }\tr M \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  } + He\left\{ \one\tr \left( \left( R + L - I \right) R^{-1} X \one - X \one \right) \right\} = \\
  &= \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  }\tr M \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  } + He\left\{ \one\tr \left( L - I \right) R^{-1} X \one \right\} < 0
\end{align*}

\begin{align*}
  \Delta V &= \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  }\tr M \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  } + \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  }\tr R_{\nu}\tr \bar{R_{\xi}}\tr 
  He \left\{ \Gamma \bar{X}  \right\} \bar{R_{\xi}} R_{\nu} \bmx{
    \tilde{x}\\
    \tilde{\psi}\\
    \tilde{\phi}
  }
\end{align*}

The matrix $\bar{R_{\xi}}$ now takes into account the non-linearity $\tilde{\phi}$, the matrix $R_{\nu}$ takes care of $\tilde{\nu}$

$$
  \bar{R_{\xi}} = \bmx{
  \begin{array}{c | c}
    R_{\xi} & 0\\
    \hline
    0 & \Id
  \end{array}
  }; R_{\nu} = \bmx{
    \Id & 0 & 0\\
    0 & \Id & 0\\
    R N_{\nu x} & \Id - R & 0\\
    0 & 0 & \Id
  }
$$

Now the previously seen sector conditions for the sin non linearities can be added in the same way as before.

\textbf{SHOULD I ADD SECTOR CONDITIONS FOR ETM OR ARE THEY ALREADY TAKEN INTO ACCOUNT INSIDE THE FINSLER CONDITIONS?}
